Explicit B-spline regularization in diffeomorphic image registration

### 2013-10-25 paper.tex
ENH: Keywords.

\title[DMFFD Diffeomorphic Image Registration]{Explicit B-spline regularization in diffeomorphic image registration}
\author[\firstAuthorLast ]{\Authors}
\address{}
\correspondance{}
\editor{}
\topic{}

@@

\begin{abstract}
Important methodological developments in the evolution of image registration algorithms include those
in which the correspondence relationship is characterized by diffeomorphisms.
The  popularity of these approaches is due largely to their
topological properties and success in providing biologically plausible
solutions to deformation and morphological
estimation problems. Popular variants of diffeomorphic algorithms include those characterized by
time-varying and constant velocity fields, and symmetrical considerations.
Prior information (i.e. regularization) is used to enforce transform plausibility taking the form of physics-based constraints or through some approximation thereof, e.g. Gaussian smoothing of the vector fields (a la Thirion's Demons \citep{thirion1998}).  In the context of the original Demons' framework, a free-form deformation methodological variant, the so-called {\it directly manipulated free-form deformation} \citep{tustison2009}, can be viewed as an alternative smoothing approach in which explicit regularization is achieved through 
fast B-spline appromixation.
This characterization can be used to provide alternative B-spline ``flavored'' diffeomorphic image registration solutions with several advantages which we describe in this work.  Implementation is open source and available through the Insight Toolkit and our Advanced Normalization Tools (ANTs) repository.  A thorough comparative evaluation with the well-known SyN algorithm \citep{avants2008}, implemented within the same framework, and its B-spline analog is performed using open data and open source evaluation tools.
\tiny
\keyFont{ \section{Keywords:}
open science, best practices, reproducibility, software }
\end{abstract}

>>>>

\title[DMFFD diffeomorphic image registration]{Explicit B-spline regularization in diffeomorphic image registration}
\author[\firstAuthorLast ]{\Authors}
\address{}
\correspondance{}
\editor{}
\topic{}

@@

\begin{abstract}
Important methodological developments in the evolution of image registration algorithms include those
in which the correspondence relationship is characterized by diffeomorphisms.
The  popularity of these approaches is due largely to their
topological properties and success in providing biologically plausible
solutions to deformation and morphological
estimation problems. Popular variants of diffeomorphic algorithms include those characterized by
time-varying and constant velocity fields, and symmetrical considerations.
Prior information (i.e. regularization) is used to enforce transform plausibility taking the form of physics-based constraints or through some approximation thereof, e.g. Gaussian smoothing of the vector fields (a la Thirion's Demons \citep{thirion1998}).  In the context of the original Demons' framework, a free-form deformation methodological variant, the so-called {\it directly manipulated free-form deformation} \citep{tustison2009}, can be viewed as an alternative smoothing approach in which explicit regularization is achieved through 
fast B-spline appromixation.
This characterization can be used to provide alternative B-spline ``flavored'' diffeomorphic image registration solutions with several advantages which we describe in this work.  Implementation is open source and available through the Insight Toolkit and our Advanced Normalization Tools (ANTs) repository.  A thorough comparative evaluation with the well-known SyN algorithm \citep{avants2008}, implemented within the same framework, and its B-spline analog is performed using open data and open source evaluation tools.
\tiny
\keyFont{ \section{Keywords:}
Advanced Normalization Tools, diffeomorphisms, directly manipulated free-form deformation, Insight Toolkit, spatial normalization }
\end{abstract}
